```{r}
install.packages("tidyverse")
install.packages("googlesheets4")
install.packages("statnet")
```


```{r}
library(googlesheets4)
library(tidyverse)
library(statnet)
```

## Read in data from google sheets


```{r}
gs4_deauth()
cleaner_name_data <-
  read_sheet(
    "https://docs.google.com/spreadsheets/d/1mS9ZOdOhL7Z0ANILpuyGnKzGsp1246THDbBfWLNVraI/edit#gid=1496824528",
    3
  )
hosts_data <-
  read_sheet(
    "https://docs.google.com/spreadsheets/d/1FTaTG3PryNbT1FnJzDftk2OpPzFtXdoe8KeNFxxb7AY/edit#gid=2083608928",
    2
  )
rs_data <-
  read_sheet(
    "https://docs.google.com/spreadsheets/d/1mS9ZOdOhL7Z0ANILpuyGnKzGsp1246THDbBfWLNVraI/edit#gid=603853676",
    5
  )

#reading in then cleaning host data
hosts_data_long <- hosts_data %>%
  separate_longer_delim(c("host", "gender"), delim = ", ")

#Making everything lowercase
hosts_data_long$host <- tolower(hosts_data_long$host)

#overwriting names_combined with real_name, then renaming column to final name
name_data <- cleaner_name_data %>%
  mutate(final_name = coalesce(real_name, names_combined))

#selecting cols of interest
static_name_data_skinny <- name_data %>%
  select("Show.Name", "final_name", "Full.Date") %>%
  left_join(., hosts_data, by = c("Show.Name" = "show")) %>%
  select("Show.Name", "final_name", "political_leaning", "Full.Date") %>%
  rename("Partisan.Leaning" = "political_leaning")

#renaming columns of host_data_long for anti join
colnames(hosts_data_long) <- c(
  "Show.Name",
  "final_name",
  "Partisan.Leaning",
  "Network",
  "guessed_gender",
  "Men.Only",
  "Top.Misinfo",
  "category",
  "show_age_months",
  "episode_days_per_month",
  "end_date",
  "start_date",
  "followers_twitter",
  "twitter_handles",
  "show_handle",
  "lean2"
)

## Read in and clean the gender data
static_name_data_skinny_cleaner <-
  anti_join(static_name_data_skinny,
            hosts_data_long,
            by = c("Show.Name", "final_name"))

# Read in data from Google Sheets
gs4_deauth() #making sure I have read permissions straightened out
static_names <- read_sheet("https://docs.google.com/spreadsheets/d/13IWciS_cxNLqlZMoYSsmdvCNnU70x2-wWIp1B4Ktw3U/edit#gid=1035186801")

#Extracting then cleaning the first name of guests
static_name_data_skinny_cleaner$name <-
  str_extract(static_name_data_skinny_cleaner$final_name, regex('^\\S*')) %>%
  trimws()

#Merging data with the edgelist, reordering columns to develop digraph
static_name_data_skinny_cleaner_p <-
  left_join(static_name_data_skinny_cleaner,
            static_names,
            by = c("name")) %>%
            drop_na(., final_name) %>% 
            group_by_all(.) %>%
            count(.) %>% 
          rename(weights=n) %>% unique(.) %>%
  .[c(2, 1, 3, 5, 6, 4, 7)] 

static_name_data_skinny_cleaner_p[is.na(static_name_data_skinny_cleaner_p$guessed_gender), 5] <- "male" #need to manually code in one missing data point!
```

## Read in data on government officials


```{r}
combined_governments <- read.csv("/home/sdemets/combined_governments.csv") %>% select(-c('X'))
congress_complete <- read.csv("/home/sdemets/congress_complete.csv") %>% select(-c('X'))
```

## Generate covariates on data
Below, we add:
- a unique **vertex id** on guests and shows in order to clearly identify who is who, which makes adding other attributes easier down the line.
- **node type** for later use, indicating if a particular node is a show or a guest. 
- Redundantly, **is actor**, for statnet (do not worry about this one).
- **is host**, to indicate if a given guest hosts their own podcast (and if the podcast is one of the shows in this dataset).
- **gender**, which is unfortunately only binary. For guests where gender cannot be estimated based on the name, gender is listed as unknown.
- **politics**. For individuals whose name match those of any federal officials, cabinet members (elected or not) in congress from 2012 to 2024. Likewise, governors and lieutenant governors are included.
- **partisan leaning** of the shows in question. These were taken from the accompanying Brookings set. Any unknowns were modified. Libertarian shows were listed as more conservative.
- The **number of followers** a given show or show host has on Twitter (now X).
- **Repeat spreader** whether a specific __guest__ has been identified by the CiP as a repeat spreader of election disinformation. For shows, we picked the top 8 offenders listed by the Brookings institute.
- **Episode frequency** the number of shows released per month, to control for variation between shows that release say daily, twice per week, or other.


```{r}
### vID #####################################################################
guest_ID <- unique(static_name_data_skinny_cleaner_p$final_name)
show_ID <- unique(hosts_data$show)
vID <- c(guest_ID, show_ID)

### node_type #####################################################################
guests <- rep("guest", length(guest_ID))
shows <- rep("show", length(show_ID))
node_type <- c(guests, shows)

### is_actor #####################################################################
is_actor <- node_type == "guest"
static_bip_nodes <- data.frame(vID, node_type, is_actor)

### is_host #####################################################################
hosts_data_long_cov <-
  hosts_data_long[str_detect(hosts_data_long$final_name, " "), ] %>%
  select("final_name", "Partisan.Leaning")
hosts_data_long_cov$final_name <-
  trimws(hosts_data_long_cov$final_name)
hosts_data_long_cov_DUMMY <-
  hosts_data_long_cov[str_detect(hosts_data_long_cov$final_name, " "), 1] %>%
  unique(.)
hosts_data_long_cov_DUMMY$is_host <- "TRUE"
static_bip_nodes <- left_join(static_bip_nodes,
                              hosts_data_long_cov_DUMMY,
                              by = c("vID" = "final_name"))

static_bip_nodes[is.na(static_bip_nodes$is_host), 4] <- FALSE

### gender_cov #####################################################################
vID_merger <- static_bip_nodes %>%
  select(1) %>%
  data.frame(.)
static_name_data_skinny_cleaner_gender <-
  static_name_data_skinny_cleaner_p[c("final_name", "guessed_gender")] %>%
  unique(.)

show_gender <- left_join(vID_merger,
                         hosts_data,
                         by = c("vID" = "show"))[[6]] %>%
  .[!is.na(.)]



guest_gender <- left_join(vID_merger,
                          static_name_data_skinny_cleaner_gender,
                          by = c("vID" = "final_name"))[[2]] %>%
  .[!is.na(.)]

static_bip_nodes$gender <- c(guest_gender, show_gender)

### politics ############################################################################
combined_governments_names <- combined_governments[c(1:2)]

long_names_political_affiliations <- rbind(hosts_data_long_cov,
                                           combined_governments_names,
                                           congress_complete) %>%
  unique(.) %>% 
  .[!is.na(.$Partisan.Leaning), ]

duplicate_names <- long_names_political_affiliations %>%
  group_by(final_name) %>%
  count(final_name) %>% 
  filter(n > 1)

duplicate_names <- long_names_political_affiliations %>%
  group_by(final_name) %>%
  count(final_name) %>% 
  filter(n > 1)

duplicated_pols <-
  semi_join(long_names_political_affiliations,
            duplicate_names,
            by = c("final_name")) %>%
  arrange(final_name) %>%
  select(final_name) %>%
  unique(.)

duplicated_pols$Partisan.Leaning <-
  c(
    "More Liberal",
    "More Liberal",
    "More Conservative",
    NA,
    "More Conservative",
    "More Conservative",
    "More Liberal",
    "More Conservative",
    "More Conservative",
    "More Conservative",
    "More Conservative",
    "More Conservative",
    "Moderate",
    "More Conservative",
    "More Conservative",
    "More Conservative",
    "More Liberal",
    "More Conservative",
    "More Conservative"
  )

duplicated_pols <- drop_na(duplicated_pols)
long_names_political_affiliations_cleaned <-
  anti_join(long_names_political_affiliations,
            duplicated_pols,
            by = c("final_name")) %>%
  rbind(., duplicated_pols)

#grab the political leaning of the show
show_political <- left_join(vID_merger,
                            hosts_data,
                            by = c("vID" = "show"))[[3]] %>%
  .[!is.na(.)]

#grab the political leaning  of the guest
guest_political <- left_join(vID_merger,
                             long_names_political_affiliations_cleaned,
                             by = c("vID" = "final_name"))[[2]] %>%
  head(.,-(length(show_political)))
static_bip_nodes$political_leaning <-
  c(guest_political, show_political) %>%
  replace_na("unknown")

#### Adding Repeat Spreader ID ###################
show_rs <-
  hosts_data[c(1, 7)]
static_bip_guest <-
  static_bip_nodes[static_bip_nodes$node_type == "guest", ]
static_bip_show <-
  static_bip_nodes[static_bip_nodes$node_type == "show", ]

rs_guest <-
  left_join(static_bip_guest, rs_data, by = c("vID" = "name")) %>%
  dplyr::mutate(is_rs = replace_na(is_rs, "no")) %>%
  select(is_rs)

rs_show <- left_join(static_bip_show, show_rs,
                     by = c("vID" = "show")) %>%
  rename(is_rs = "in_AR_OR_RS") %>%
  dplyr::mutate(is_rs = replace_na(is_rs, "no")) %>%
  select(is_rs)

is_misinfo_rs <- bind_rows(rs_guest, rs_show)
static_bip_nodes <- bind_cols(static_bip_nodes, is_misinfo_rs)

##### Adding Episode Frequency per Month ##############
guest_frequency <- rep(NA, length(guest_ID))
ep_freq <-
  static_bip_nodes %>%
  filter(is_actor == "FALSE") %>%
  left_join(., hosts_data, by = c("vID" = "show")) %>%
  select(episode_days_per_month)
sf <- c(guest_frequency, ep_freq$episode_days_per_month)
static_bip_nodes$ep_freq <- sf

##### Adding Number of Followers #######
host_l <- rep(NA, length(guest_ID))
host_followers <- static_bip_nodes %>%
  filter(is_actor == "FALSE") %>%
  left_join(., hosts_data, by = c("vID" = "show")) %>%
  select(followers)
hf <- c(host_l, host_followers$followers)
static_bip_nodes$host_followers <- hf
```

## Create the bipartite network of shows and guests. Additionally, create a one mode network of the same data.


```{r}
### Create edgelist
static_bip_edges <- static_name_data_skinny_cleaner_p %>%
                    ungroup(.) %>% 
                    select(1,2,3,5) %>%
                    rename(actor = final_name, 
                           event = Show.Name) %>%
                     unique(.)

# create bipartite net
static_bip_net <- as.network(static_bip_edges,
  directed = FALSE, vertices = static_bip_nodes,
  bipartite = TRUE, multiple = FALSE
)

# create one mode net
omp <- as.network(static_bip_edges,
  directed = TRUE, vertices = static_bip_nodes, multiple = FALSE
)
```

## Create the show/show projection of at least 1 common guest, then 2 common guests, then cross-cutting guests.


```{r}
coengaged_hosts <- static_name_data_skinny_cleaner %>%
  group_by(final_name) %>%
  expand(Show.Name, Show.Name) %>%
  .[.$Show.Name...1 != .$Show.Name...2,] %>%
  ungroup(.) %>% 
  drop_na(.) %>% 
  relocate(2,3,1) %>%
  group_by(Show.Name...1, Show.Name...2) %>% 
  summarize(final_name = paste0(final_name, collapse = ", "))


#Deleting duplicated edges
coengaged_hosts$temp <- apply(coengaged_hosts, 1, function(x) paste(sort(x), collapse=""))
coengaged_hosts <- coengaged_hosts[!duplicated(coengaged_hosts$temp), 1:3]

#converting edgelist to network, then adding missing vertices                              
static_host_projection <- network(coengaged_hosts, matrix.type = "edgelist", directed = FALSE, multiple = FALSE)
missing_nodes <- setdiff((unique(hosts_data$show)), (static_host_projection%v%'vertex.names'))
static_host_projection <- add.vertices(static_host_projection, length(missing_nodes))

#Adding vertex names to missing vertices                              
missing_node_ids <- which(is.na(static_host_projection%v%"vertex.names"))
for(i in 1:length(missing_node_ids)){
    set.vertex.attribute(static_host_projection, "vertex.names", missing_nodes[[i]], missing_node_ids[i])
    } 
```


```{r}
#This is almost the exact same process as above, just run on filtered data from the first step
coengaged_hosts_2 <- static_name_data_skinny_cleaner %>%
  group_by(final_name) %>%
  expand(Show.Name, Show.Name) %>%
  .[.$Show.Name...1 != .$Show.Name...2,] %>%
  select(-c(final_name)) %>%
  ungroup(.) %>% 
  drop_na(.) %>%  
  select(-c(final_name)) %>%
  group_by_all(.) %>% count(.) %>%
  filter(n>1) %>% #selecting for guests who have appeared more than once
  select(-c(n))

#getting rid of duplicated edges then adding missing vertices
coengaged_hosts_2$temp <- apply(coengaged_hosts_2, 1, function(x) paste(sort(x), collapse=""))
coengaged_hosts_2 <- coengaged_hosts_2[!duplicated(coengaged_hosts_2$temp), 1:2]                            
static_host_projection2 <- network(coengaged_hosts_2, matrix.type = "edgelist", directed = FALSE, multiple = FALSE)
                                
#Add missing vertices and their corresponding names                                
missing_nodes2 <- setdiff((unique(hosts_data$show)), (static_host_projection2%v%'vertex.names'))
static_host_projection2 <- add.vertices(static_host_projection2, length(missing_nodes2))                            
missing_node_ids2 <- which(is.na(static_host_projection2%v%"vertex.names"))
                                
for(i in 1:(length(missing_node_ids2))){
    set.vertex.attribute(static_host_projection2, "vertex.names", missing_nodes2[[i]], missing_node_ids2[i])
    }
```


```{r}
coengaged_hosts_mismatches <- left_join(coengaged_hosts,
                                        hosts_data,
                                        by = c("Show.Name...1" = "show")) %>%
  select(c(1, 2, 3, 4, 5, 6))

coengaged_hosts_mismatches <- left_join(coengaged_hosts_mismatches,
                                        hosts_data,
                                        by = c("Show.Name...2" = "show")) %>%
  filter(political_leaning.x != political_leaning.y) %>%
  select(c(1, 2, 3))

bridge_guests <- data.frame(coengaged_hosts_mismatches) %>%
  separate_longer_delim(3, delim = ", ") %>%
  group_by_all(.) %>%
  count(.) %>% 
  ungroup(.) %>% 
  unique(.)

bridge_guests$Show <- paste(bridge_guests$Show.Name...1,
        bridge_guests$Show.Name...2,
        sep = "_")

mm_projection <- bridge_guests %>% 
    select(c("Show.Name...1",
             "Show.Name...2",
             "final_name")) %>% 
    network(., 
            matrix.type = "edgelist", 
            directed = FALSE, 
            multiple = TRUE)
```


```{r}
############ adding covariates to the complete show/show coengagement network ###############
add_show_show_cov <- function(g){
    host_coengaged_shows_names <- data.frame(show = g%v%'vertex.names')
    host_leaning_data <- hosts_data %>% select(-c(host))
    host_leaning_data_full <- inner_join(host_coengaged_shows_names, 
                                         host_leaning_data, by = c("show"))
    g%v%'partisan_leaning' <- host_leaning_data_full$political_leaning
    g%v%'network' <- host_leaning_data_full$Network
    g%v%'gender' <- host_leaning_data_full$only_men
    g%v%'top_misinfo' <- host_leaning_data_full$in_AR
    g%v%'category' <- host_leaning_data_full$category
    g%v%'show_age' <- host_leaning_data_full$show_age_months
    g%v%'episode_frequency' <- host_leaning_data_full$episode_days_per_month
    g%v%'followers' <- host_leaning_data_full$followers
    return(g)
    }

static_host_projection <- add_show_show_cov(static_host_projection)
static_host_projection2 <- add_show_show_cov(static_host_projection2)
mm_projection <- add_show_show_cov(mm_projection)
```

## Write data to files in networks


```{r}
write.csv(static_name_data_skinny_cleaner_p, "/home/sdemets/Apple_Podcast_Political_Data/network_data/full_network_dataframe.csv")
saveRDS(static_bip_net, "/home/sdemets/Apple_Podcast_Political_Data/network_data/static_bip.rds")
saveRDS(static_host_projection, "/home/sdemets/Apple_Podcast_Political_Data/network_data/static_host_projection.rds")
saveRDS(mm_projection, "/home/sdemets/Apple_Podcast_Political_Data/network_data/mm_projection.rds")
```

## Update specific file
This is needed to run if I have updated/cleaned any of the Apple guests data.


```{r}
#Define the file(s) that you want to update
fn <- "/home/sdemets/Apple_Podcast_Political_Data/network_data/full_network_dataframe.csv"
#Check its existence
if (file.exists(fn)) {
    #Delete file if it exists
    file.remove(fn)
}
```

## DO NOT RUN! Code used to generate the gender data.
Partially commented out so it doesn't work.

```{r}
#remotes::install_github("lmullen/genderdata")
#install.packages("gender")
#library(gender)
#library(genderdata)

#Extracting then cleaning the first name of guests
#static_name_data_skinny_cleaner$name <-
  str_extract(static_name_data_skinny_cleaner$final_name, regex('^\\S*')) %>%
  trimws()

print("Done!")
# Get unique names then rename column
#static_names <-
  #data.frame(unique(static_name_data_skinny_cleaner$name)) %>%
  rename("name" = "unique.static_name_data_skinny_cleaner.name.")

print("Done!")
#Generating an empty variable to fill
guessed_gender <- rep("unknown", nrow(static_names))

print("Done!")

#For loop to ID gender using the gender package.
for (i in 1:nrow(static_names)) {
  print(i)
  tryCatch({
    print(i)
    guessed_gender[[i]] <- gender(static_names[[i, 1]], countries = c("United States"))[[4]]
    print(i)
  #},
  error = function(e) {
    print(i)
    guessed_gender[[i]] <- NA
  })
}

#Saving data in the data frame
static_names$guessed_gender <- guessed_gender
```
